---
title: '#CampFire Twitter Trends'
author: "Math 685 students"
date: "10/25/2019"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(rtweet)

set.seed(1067)
theme_set(theme_minimal())
```

Refs
* Official Docs: https://rtweet.info/
* http://www.storybench.org/get-twitter-data-rtweet-r/
* http://rpubs.com/petermcnamara/481358





# Full historical search

* get historical tweets https://stackoverflow.com/questions/56413157/downloading-historical-tweets-via-rtweet-from-premium-api-via-r
* Official docs on how to get started: https://developer.twitter.com/en/docs/tweets/search/quick-start/premium-full-archive

Get bearer token
https://developer.twitter.com/en/docs/basics/authentication/guides/bearer-tokens

* Save this info into a .txt file and **add this file to the gitignore**. This should not be public!

```{r}
twitter_token <- create_token(
  app="campfiredata", 
  consumer_key = "QlOOA0zePLxsvKg7FtxtmhAYC", 
  consumer_secret = "qHzRIxXGpuo0DClC0kCjC65XBANnBfnqfBNPQZvl3Ju4WA1gef", 
  access_token = "572383090-JJF2uD61U0vXUQ38vtUDO1pXmPZCCznYVS759wYm",
  access_secret = "RnUthduVcLwuPNenqQq5KL2CHd7moKgyFpiGtYgG65KJi"
)
```

```{r}
r.token <- readRDS("firetweetdata/twitter_token.Rds")
```

```{r}
test <- search_fullarchive("fire", 
                           n=100, 
                           env_name="campfiredata", 
                           fromDate = "20181108", 
                           toDate = "20181109", 
                           parse=TRUE,
                           token=r.token)
```
_not a valid access token_


Get tweets
```{r}
cf <- search_fullarchive(
  q = "#CampFire",
  n=100,
  fromDate= "20181108", 
  toDate = "20181208", 
  env_name = "campfiredata", 
  safedir = "firetweetdata/", 
  parse=TRUE, 
  token="AAAAAAAAAAAAAAAAAAAAAK1KAgEAAAAAoAXFcTvwiKE4t%2FaK9lIrDlan7Mg%3DVSwTYystHE9tAdRs7wt75oPawd3576aUBiUiBIvKSP3Rq7voLO"
)
```
_not working_

> initial example query looking for the term rtweet, filtering for tweets associated with news, excluding retweets and replies, starting on July 1, 2006 and ending on July 2, 2019

`query <- "rtweet filter:news -filter:retweets -filter:replies since:2006-07-01 until:2019-07-02"`


```{bash}
  
curl --request POST \
  --url https://api.twitter.com/1.1/tweets/search/fullarchive/campfiredata.json \
  --header 'authorization: Bearer AAAAAAAAAAAAAAAAAAAAAK1KAgEAAAAAoAXFcTvwiKE4t%2FaK9lIrDlan7Mg%3DVSwTYystHE9tAdR
s7wt75oPawd3576aUBiUiBIvKSP3Rq7voLO' \
  --header 'content-type: application/json' \
  --data '{
                "query":"fire",
                "fromDate":"20181108", 
                "toDate":"20181109",
                "maxResults":"10"
                }' \
  -o file1.json
                


curl -verbose -X POST "https://api.twitter.com/1.1/tweets/search/fullarchive/campfiredata.json" -d '{"query":"TwitterDev "search api"","maxResults":"10","fromDate":"20181108","toDate":"20181109"}' -H "Authorization: Bearer AAAAAAAAAAAAAAAAAAAAAK1KAgEAAAAAoAXFcTvwiKE4t%2FaK9lIrDlan7Mg%3DVSwTYystHE9tAdR
s7wt75oPawd3576aUBiUiBIvKSP3Rq7voLO" -o file1.json
```



